---
title: "Probability"
author: "Group 4 - Zehra, Ceren, Mehmet, Selim, Berke"
date: "5 Ekim 2017"
output:
  pdf_document: default
  word_document: default
---

# Question 1
A die is thrown once.What is the probability that upper surface has a prime number?

```{r}
# The prime numbers are 2, 3 and 5 so;
n1=3 # number of ways it can happen
n2=6 #The Total number of outcomes

#Probability of an event happening = The Number of ways it can happen/The Total number of outcomes 

n1/n2 # The probability of a prime number
```

# Question 2
There are three seats left in a plane and there are 5 people who wants to get a ticket. If you want to choose three people at once, how many different ways can you arrange their seats ?

```{r}
n1=5 # number of people who but a ticket
n2=3 # empty seats left
n3=3 #how many people you are chooseing at once
(factorial(n1)*factorial(n2)) / (factorial(n3) * factorial(n1-n3))
```

# Question 3
In a chest, ther are 7 red, 5 blue and 9 green balls. If we picked 3 balls, what is the probability of 3 different colours?
```{r}
n1=7# number of red
n2=5 # number of blue
n3=9 # number of gren
n4= n1+n2+n3
(n1/n4) * (n2/(n4-1)) * (n3/(n4-2))
```