---
title: "Homework 1 - IE 231 Fall"
author: "Group 5 - Hakan Balay - Duygu Aras - Mısra Şimşir - Şebnem Çilek - Fikret Gizem Keçeli"
date: "05 10 2017"
output: word_document
---
##Question 1:

What is the probability of getting a sum 9 from two throws of a dice?

Solution: nEvent/n1*n2 <- 4/36

```{r}
n1 <- 6 #die roll has six potential outcomes.
n2 <- 6 #die roll has six potential outcomes.
nEvent <- 4 #event of getting a sum which are (3,6) , (4,5) , (5,4) , (6,3).

nEvent/prod(n1,n2)
```

##Question 2:

A committee of 4 persons are to be formed from the club members consisting 20 men and 15 women. What is the probability of a committee consisting 2 men and 2 women is formed?

Solution: Combination Rule!

```{r}
n_clubmembers <- 4 #number of club members
n_comittee <- 4 #number of comittee which sould
n_men <- 20 #number of men
n_women <- 15 #number of women

n_ss <- choose(35,4) #Number of sample space
n_com <-choose(20,2) #Number of event of choosing 2 people from men
n_cow <-choose(15,2) #Number of event of choosing 2 people from women

prod(n_com,n_cow)/n_ss
```

##Question 3:

A packet contains similar size of cards labeled as A,B,C,D and E. Three cards are picked up one by one at random and placed on the same order. What is the probability that the word formed by those letters is BAD?

Solution: Factorial!

```{r}
the_phrase <- "ABCDE"
freq_table <- table(strsplit(the_phrase,split="")[[1]]) #Creating a frequency table in order to control repeating letters
print(freq_table) #Printing frequency table
letter_length <- 3 #Number of letter words which we want create
n_ss <- factorial(nchar(the_phrase))/factorial(nchar(the_phrase)-letter_length) #Number of sample space
n_event <- 1 #Number of event which is "BAD"
print(n_event) #Printing event
print(n_ss) #Printing sample space
n_event/n_ss
```