---
title: "Some Problems about Basic Probability and Counting"
author: "IE231 - Lecture Notes 2"
date: "06 10 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1
Suppose a coin is flipped 3 times. What is the probability of getting two tails and one head?

Solution: The sample space consists of 8 sample points.

A= {TTT, TTH, THT, THH, HTT, HTH, HHT, HHH}

Each sample point is equally likely to occur, so the probability of getting any particular sample point is 1/8. The event "getting two tails and one head" consists of the following subset of the sample space.

B = {TTH, THT, HTT}

The probability of Event B is the sum of the probabilities of the sample points in B. Therefore,

P(B)) = 1/8 + 1/8 + 1/8 = 3/8

```{r}
#We are supposing that the coin is flipped 3 times.
#Permutation Rule 
factorial(2)*factorial(2)*factorial(2)

```

```{r}
#Probability of the evet getting two tails and one head" .
n1 <- 1/8 #the probability of getting any particular sample point
n2 <- 1/8 #the probability of getting any particular sample point
n3 <- 1/8 #the probability of getting any particular sample point

(n1+n2+n3) #the total
```


#Question 2

There are 50 students in a language school; 15 students from Germany, 17 students from Turkey, 18 students from France.Suppose that you want to form a group of 10 people with at least 1 students from each of them.In how many way can you form such a class?

Solution: Calculate as if no rules.It is the combination of 50 to 10.Then remove the combinations of all Germany or all France or all Turkey people.

```{r}
#Combination Rule
choose(50,10)-choose(15,10)-choose(17,10)-choose(18,10)
```



#Question 3 

How many numbers that are between 2 and 4 digits (including 2,4) also can be divided by 5 and be formed from the numbers; 3,2,5,7,0,9 such that non of them repeats?

Solution: In order to be divided by 5, number must be end with 5 or 0. One of the most important points is that zero the number should not be placed as a first digit.Order is not important for the form so use combination.Last thing is to sum all of the possible outcomes.

```{r}
#Combination Rule for 5 as a last digit; for 2 digits
n1 <- choose(4,1)+(choose(4,1)*choose(4,1))+(choose(4,1)*choose(4,1)*choose(3,1))

```


```{r}
#Combination Rule for 0 as a last digit; for 2 digits
n2 <- choose(5,1)+(choose(5,1)*choose(4,1))+(choose(5,1)*choose(4,1)*choose(3,1))

```

```{r}
#Let's sum all the possible outcomes.
n1+n2
```



