---
title: "Group 1 Homework 1"
author: "Emre Akçöl,Deniz Uysal,Naz Uziyel,Serra Þimþir,Helin Göncü,Kaan Zengi"
date: "5 Ekim 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1

There are 11 middlefielders in a football team. In how many ways 4 of them can be chosen to play in a match?

Solution: Combination rule since the order is not important. 
C(11,4) = 11!/(4!(11-4)!) = 330

```{r}
#Combination Rule
choose(11,4)
```


#Question 2 

If we want to change the order of letters in the word "KELEBEK" how many of words with seven letters finish with "LEB"?

Solution: We are going to think about it like "_ _ _ _ L E B" Also remember the permutation rule with identical items. There are 2 "K"s and 3 "E"s. However, one of the "E" is in the "L E B" so we are going to take it "E"s as 2. 
The formula is n(number of spaces)! / n1!n2!...nk! 
So the result is: 4!/2!2! = 24/4 = 6 

```{r}
the_phrase <- "KELEBEK"  #The word
freq_table <- table(strsplit(the_phrase,split="")[[1]]) #We are going to create a frequency table
print(freq_table) 

```

```{r}
the_phrase <- "KEKE" #Letters which we can put to spaces
freq_table <- table(strsplit(the_phrase,split="")[[1]]) # Frequency table for the usable letters
print(freq_table) #Let's show it
```


```{r}
the_dividend <- factorial(nchar(the_phrase)) #Dividend part is 4 characters so 4!
the_divisor <- prod(factorial(freq_table)) #Get multiplication of factorials for the divisor
the_dividend/the_divisor
```


#Question 3 

The %40 of the students are girls in a class. %50 of boys and %70 of girls have failed. It is known that a randomly selected student in the class has passed the class. What is the probability of that student is a boy?

Solution: Remember that, probability is never greater than 1. Let's say that the sum of boys and the girls in the class is 100. So 40 students are girls and only 12 of them has passed the class. This information also give us 60 students are boys and only 30 of them has passed the class. 
So the result is: 30/42 = 5/7 = 0.7142857

```{r}
#We said that class is 100 people as an assumption.
n_student <- 100
n_girls <-40
n_boys <-60
```

```{r}
#Let's find the number of boys who passed the class.
n_boys <- 60
the_dividend <-60
the_divisor  <- 2 # Because only half of them passed the class
the_dividend/the_divisor
```

```{r}
#Let's find the number of girls who passed the class.
n_girls <- 40
the_ratio  <- 30/100 # Because only %30 of them passed the class
n_girls*the_ratio
```

```{r}
n1 <- 30 #Number of boys who passed the class
n2 <- 12 #Number of girls who passed the class

n1/(n1+n2)
```





