---
title: "Week2submission"
author: "Group2- Utku Özer Coşkun-Dilara Bennani Ziatni-Ege Pekseren-Ege Ebiller"
date: "5 Ekim 2017"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Question1
1)basketball team has 12 players. A photo will be taken after this team becomes champion. How many different ways can this team be ordered?
Solution: Permutation rule. $n! = 12! = 479001600$

```{r}
n_players <- 12 #Number of teletubbies
factorial(n_players) #By permtuation it is 12!
```
##Question2
2)We want to reorder the letters of the phrase "KUYRUKSALLAYANGİLLER". In how many ways can we do it?
```{r}
the_phrase <- "KUYRUKSALLAYANGİLLER"
freq_table <- table(strsplit(the_phrase,split="")[[1]]) #Let's create a frequency table first
print(freq_table) #Let's show it
the_dividend <- factorial(nchar(the_phrase)) #Dividend part is 20 characters so 20!
the_divisor <- prod(factorial(freq_table)) #Get multiplication of factorials for the divisor
the_dividend/the_divisor
```
##Question3
3)There are 40 seats on an airplane. 6 are business seats. if i want to get 3 seats economically. How many different ways can I choose?

```{r}
#Combination function is choose for 3 seats in 34 seats.
choose(34,3)
```
