---
title: "Homework 1-IE 231 Fall 2017"
author: "Group 3-Sevval Kartal-Erkmen Sezer-Ekin Deren Altuncu-Seyda Nur Bici-Emre Gelgec"
date: "10/5/2017"
output: word_document
---
## Question 1
The basketball league in one city has got eight teams.Calculate the number of prediction for top three,in order,teams at the end of season.

```{r}
#It is multiplication rule
n1 = 8 #In first place there can be 8 different teams.
n2 = 7 #In second place there can be 7 different teams not 8 because on of them will be in first place.
n3 = 6 #In third place there can be 6 different teams.
n1*n2*n3
```
##Question 2
Find the number of different ways of placing 25 balls in a row given that  are 9 red,3 are yellow,6 are black and 7 are blue.

```{r}
#Permutation rule
#9 red,3 yellow,6 black,7 blue
factorial(25)/factorial(9)*factorial(3)*factorial(6)*factorial(7)

```

##Question 3
In a company,from a group of 9 men and 8 women,seven people are to be selected to join conference so that at least 5 men are there on the comittee.In how many different ways are there?

```{r}
#Combination rule
#c(9,5)*c(8,2)+c(9,6)*c(8,1)+c(9,7)*c(8,0)
#First option is 5 men and 2 women,second one is 6 men and 1 women,last option is 7 men and no women.

choose(9,5)*choose(8,2)+choose(9,6)*choose(8,1)+choose(9,7)*choose(8,0)

```


